---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(fishobspgr)
```

# fishobspgr

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/poissonconsulting/fishobspgr/workflows/R-CMD-check/badge.svg)](https://github.com/poissonconsulting/fishobspgr/actions)
[![Codecov test coverage](https://codecov.io/gh/poissonconsulting/fishobspgr/branch/main/graph/badge.svg)](https://app.codecov.io/gh/poissonconsulting/fishobspgr?branch=main)
[![License: MIT](https://img.shields.io/badge/License-MIT-green.svg)](https://opensource.org/license/mit/)
<!-- badges: end -->

`fishobspgr` is an R package that uses the `pgfeatureserv` package to query BC [fish observation](https://features.hillcrestgeo.ca/bcfishobs/) and [fish passage](https://features.hillcrestgeo.ca/bcfishpass/) web APIS.

## Installation

You can install the development version of fishobspgr from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("poissonconsulting/fishobspgr")
```

## Introduction
### Get Information on Collections

Get information about the [observation collections](https://features.hillcrestgeo.ca/bcfishobs/), [passage collections](https://features.hillcrestgeo.ca/bcfishpass/) or a collection's properties:  

* [`fop_collections_observation()`](https://poissonconsulting.github.io/fishobspgr/reference/fop_collections_observation.html)  
* [`fop_collections_passage()`](https://poissonconsulting.github.io/fishobspgr/reference/fop_collections_passage.html)  
* [`fop_collection_observation_properties()`](https://poissonconsulting.github.io/fwapgr/reference/fop_collection_observation_properties.html)  
* [`fop_collection_passage_properties()`](https://poissonconsulting.github.io/fwapgr/reference/fop_collection_passage_properties.html)  

### Query a Collection

Query features from a [observation collection](https://features.hillcrestgeo.ca/bcfishobs/collections.html) or [passage collection](https://features.hillcrestgeo.ca/bcfishpass/collections.html):  

* [`fop_query_collection_observation()`](https://poissonconsulting.github.io/fishobspgr/reference/fop_query_collection_observation.html)  
* [`fop_query_collection_passage()`](https://poissonconsulting.github.io/fishobspgr/reference/fop_query_collection_passage.html)  

## Demonstration

Query fish observation events from 'CLAY' watershed group with species code 'CO'.
```{r}
collection_id <- "bcfishobs.fiss_fish_obsrvtn_events_sp"
filter <- list(species_code = "CO", watershed_group_code = "CLAY")

x <- fop_query_collection_observation(collection_id, filter = filter)
x[1:5, 1:5]
```

## Code of Conduct

Please note that the fishobspgr project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
